\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=2.5cm]{geometry}
\usepackage{inconsolata} % Font monoespaiada agradable
\usepackage[dvipsnames]{xcolor} % Colors macos
\usepackage{tcolorbox}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue}
\usepackage{fancyvrb} % per mostrar codi

\definecolor{mykeyword}{rgb}{0.0, 0.5, 0.0}       % verd per a keywords
\definecolor{mytype}{rgb}{1.0, 0.65, 0.0} % groc taronja fort


\definecolor{myfunction}{rgb}{0.0, 0.4, 0.7}       % blau per a noms de funció
\definecolor{myconst}{rgb}{0.6, 0.1, 0.1}          % vermell fosc per a constants
% Bloc de codi configurat amb colors
\usepackage{listings}
\lstset{
	inputencoding=utf8,
	extendedchars=true,
	literate=
	{à}{{\`a}}1
	{è}{{\`e}}1
	{é}{{\'e}}1
	{í}{{\'i}}1
	{ï}{{\"i}}1
	{ò}{{\`o}}1
	{ó}{{\'o}}1
	{ú}{{\'u}}1
	{ü}{{\"u}}1
	{ç}{{\c{c}}}1
	{ñ}{{\~n}}1
	{Á}{{\'A}}1
	{É}{{\'E}}1
	{Í}{{\'I}}1
	{Ï}{{\"I}}1
	{Ó}{{\'O}}1
	{Ú}{{\'U}}1
	{Ü}{{\"U}}1
	{¿}{{?``}}1
	{¡}{{!``}}1
}
\usepackage{tcolorbox}

\tcbuselibrary{listings, skins, breakable}


\newtcblisting{metaoutput}{
	listing only,
	title=github.com/nassaba-ai/project-assimov - AI-enhanced Content Generation Pipeline,
	coltitle=black,
	breakable,
	enhanced,
	colback=white,
	colframe=white!75!black,
	sharp corners,
	listing options={
		basicstyle=\ttfamily\small,
		keywordstyle=\color{mykeyword}\bfseries,
		stringstyle=\color{BurntOrange},
		commentstyle=\color{gray},
		identifierstyle=\color{black},
		emph={phase_0_prompt_intake, phase_1_generate_structure,
			phase_2_expand_sections, phase_3_refine_coherence,
			phase_4_compile_tex, phase_5_final_review},
		emphstyle=\color{myfunction},
		emph={[2]Path, plan, tex, yamls},
		emphstyle={[2]\color{mytype}},
		emph={[3]True, False, None},
		emphstyle={[3]\color{myconst}},
		morekeywords={import, from, def, return, if, else, class, for, while},
		numbers=left,
		numberstyle=\tiny\color{gray},
		numbersep=5pt,
		xleftmargin=2.2em,
		breaklines=true
	}
}

\definecolor{mygray}{gray}{0.45}
\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{myorange}{rgb}{0.8,0.4,0}

\title{}
\author{}
\date{}

\begin{document}


\noindent
\ttfamily
\textcolor{mygreen}{\textbackslash documentclass}\textcolor{black}{[12pt,a4paper]\{article\}}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{[utf8]\{inputenc\}}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{[english]\{babel\}}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{[margin=2.5cm]\{geometry\}}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{\{inconsolata\}} \textcolor{mygray}{\%\ Pleasant monospaced font}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{\{hyperref\}}\\
\textcolor{mygreen}{\textbackslash hypersetup}\textcolor{black}{\{colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue\}}\\
\textcolor{mygreen}{\textbackslash usepackage}\textcolor{black}{\{fancyvrb\}} \textcolor{mygray}{\%\ for displaying code}

\medskip

\noindent\textcolor{mygreen}{\textbackslash title}\textcolor{black}{\{PROJECT ASSIMOV: A Manifesto for Educators in the Age of Transformers\}}\\
\textcolor{mygreen}{\textbackslash author}\textcolor{black}{\{Dídac Valenciano Gener\}}\\
\textcolor{mygreen}{\textbackslash date}\textcolor{black}{\{May 2025\}}

\medskip

\noindent\textcolor{mygreen}{\textbackslash begin}\textcolor{black}{\{document\}}\\
\textcolor{mygreen}{\textbackslash section*}\textcolor{black} \{\sffamily 2025 is — and will be — the year of ChatGPT.\}\\

				
\medskip

In Iberian and Mediterranean Europe —still shaped by a latent mecha subconscious— \emph{Mazinger Z} left a cultural and emotional imprint that marked an entire generation. For those aged 45 to 60, it’s all still there: the battle cry “\emph{¡Puños fuera!}”, the survival of \emph{Blandiblú}, the \emph{Famobil Clicks}, and afternoons filled with violent cartoons — without turning into psychopaths.

\medskip

In the United States, \emph{Hasbro} led a generational shift with the rise of the \emph{Transformers}. The saga hit its cultural peak in 2007, when, in the opening scenes, the \emph{Decepticons} attacked a U.S. military base in the Qatari desert.

\medskip

\emph{Megan Fox} and \emph{Shia LaBeouf} stole the spotlight — but something else stayed with us.

\medskip

A small \emph{Decepticon} — a \emph{Transformer}, but one of the bad ones — hides in plain sight among the protagonists’ things. It absorbs metal, mutates, stretches, elongates, adapts. Until it becomes what it needs to be.

\bigskip

Ten years later, as the result of a long research journey — by both academic and private entities — and in parallel with the entertainment world, \emph{Google} publicly introduced, in 2017, an algorithmic technology.

\medskip

One that replicates itself. Stretches. Expands its own structure. Modifies and elongates — until, purely by probability, it reaches its goal.

\medskip

What a surprise — and what a coincidence — that this technology, previously unknown, was named: \emph{transformers}.

\bigskip

And the beauty of it, my friends, is this: it simulates so well.

\medskip

If we define \emph{artificial intelligence} as a functional simulation of intelligence... well, there might be other implementations.

\medskip

But this one — definitely — is one.

\bigskip

What follows is another implementation.

\medskip

One that, like the algorithms from \emph{OpenAI}, stretches, adapts, and reshapes itself — all to generate, in a purely probabilistic way, the best possible answer to the task ahead.

\medskip

In this case? Creating content. Didactic material. Articles. Maybe even a book.

\medskip

So that we, \emph{teachers}, have our own tools — ready for the battle that lies ahead.  

\medskip

We got all the weapons we need: Now fight!  \hfill\textit{(Sucker Punch — 2011)}

\newpage
			
			\begin{metaoutput}
# Phase 0: Interpret prompt and assign roles with grammarnaut + llm_router

# Phase 1: Generate structural skeleton with yaml_generator using Claude or o3 or ...

# Phase 2: Expand each section with role-assigned LLMs (GPT-4o, MythoMax, Lit-6B...) using cached YAMLs

# Phase 3: Review narrative coherence, argument and tone with o3 or Claude using section context

# Phase 4: Compile formatted output into .tex with writer or translator

# Phase 5 (optional): Final stylistic polish by purist LLM or human reviewer

###################################################
# AI-enhanced Content Generation Pipeline (Assimov)

import openai
from pathlib import Path
import time

def phase_0_prompt_intake():
    """Receive user prompt and determine functional roles + LLMs."""
    prompt = user_input()
    roles = assign_roles(prompt)  # via gramaneute.py -> llm_router.py
    llms = select_models(roles, config="config.yaml")
    return plan(roles, llms)

def phase_1_generate_structure(plan):
    """Create YAML skeleton per section with titles, themes, targets."""
    yamls = []
    for section in plan.sections:
    yamls.append(generate_yaml(section))  # via yaml_generator.py or real LLM
    return yamls

def phase_2_expand_sections(yamls):
    """Expand each section via assigned LLM, using cached context."""
    content = []
    for yaml in yamls:
        llm = yaml.assigned_model
        section_text = expand_from_yaml(yaml, llm=llm, use_cache=True)
        content.append(section_text)
    return content

def phase_3_refine_coherence(content):
    """Polish narrative flow, argument structure, and tonal coherence."""
    polished = []
    for section in content:
        coherent = enforce_coherence(section)  # coherence supervisor
        refined = polish_argument(coherent)
        toned = adjust_tone(refined)
        polished.append(toned)
    return polished

def phase_4_compile_tex(polished):
    """Format polished content into a .tex document with structure."""
    doc = initialize_tex()
    for section in polished:
        doc.append(format_section(section))  # via writer.py or translator.py
    return doc

def phase_5_final_review(tex_document):
    """Optional: stylistic and poetic pass by a purist LLM or human."""
    reviewed = manual_review(tex_document)
    return reviewed

# Main pipeline execution

if __name__ == "__main__":
    plan = phase_0_prompt_intake()
    yamls = phase_1_generate_structure(plan)
    raw_content = phase_2_expand_sections(yamls)
    refined = phase_3_refine_coherence(raw_content)
    tex = phase_4_compile_tex(refined)
    final_output = phase_5_final_review(tex)
    save(final_output, "output/document.tex")			
			\end{metaoutput}
\noindent
\textit{This work is licensed under a Creative Commons Attribution – NonCommercial – ShareAlike 4.0 International License (CC BY-NC-SA 4.0).}\\
\url{https://creativecommons.org/licenses/by-nc-sa/4.0/}			
		\end{document}
