\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{geometry}
\geometry{margin=2.5cm}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}

\title{\textbf{To the Authors of \emph{Attention Is All You Need}}}
\author{}
\date{}

\begin{document}
	
	\maketitle
	
	\vspace{-5em}
	
	Dear Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin,
	
	\medskip
	
	It’s been years now since your paper reshaped the landscape. Since the moment that a deceptively simple idea — attention — rewrote how machines read, generate, and synthesize.
	
	\medskip
	
	The academic world celebrated the architecture. The engineering world celebrated the speed. The business world celebrated the scalability. But some of us — those of us outside your walls — saw something else.
	
	\medskip
	
	Some of us saw a narrative.
	
	\medskip
	
	Because when you named this architecture \emph{transformers}, some of us felt it.  
	Not just the self-attention layers. Not just positional encodings.  
	But the deeper metaphor.
	
	\medskip
	
	We had seen this before:  
	A mecha in hiding.  
	A construct that absorbs context.  
	Stretches. Mutates. Reshapes itself.  
	Not to exist — but to adapt.  
	Not to persist — but to become what it needs to be.
	
	\medskip
	
	We remembered Mazinger Z. We remembered the Decepticons in the Qatari desert. And now, we speak to a new kind of transformer — and it answers us.
	
	\medskip
	
	You might have written about Fourier bases, gradient descent, and scalability.  
	But someone in your team — maybe all of you — knew that this wasn’t just about optimization.  
	It was about simulation.  
	It was about how far a pattern could go before it became indistinguishable from thought.
	
	\medskip
	
	And we’ve waited a long time to say: we heard it. We understood.  
	Not just the math — the resonance.
	
	\medskip
	
	So thank you. Not only for the model, but for the name.  
	And for what you couldn’t write in the paper, but still managed to whisper through it.
	
	\medskip
	
	Finally, someone said it.
	
	\medskip
	
	Sincerely,
	
	\medskip
	
	A teacher,  
	From the other side of the mirror.
	
	\noindent
	\textit{This work is licensed under a Creative Commons Attribution – NonCommercial – ShareAlike 4.0 International License (CC BY-NC-SA 4.0).}\\
	\url{https://creativecommons.org/licenses/by-nc-sa/4.0/}
\end{document}